\textit{Supplemental materials for:} High-level cognition is supported by information-rich but compressible brain activity patterns

### 2024-03-11 paper/supplement.tex
title change
submitted version (PNAS R2)
adding autocorrelation analysis (will remove later)
added autocorrelation analysis

\title{\textit{Supplemental materials for:} High-order cognition is supported by information-rich but compressible brain activity patterns}

@@

@@

\newpage
\renewcommand{\refname}{Supplemental references}
\bibliographystyle{apacite}
\bibliography{CDL-bibliography/cdl}

>>>>

\title{\textit{Supplemental materials for:} High-level cognition is supported by information-rich but compressible brain activity patterns}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{figs/autocorrelations}

\caption{\textbf{Autocorrelations.} \textbf{A. Temporal autocorrelations.} The
panel displays the average correlation (taken across all nodes and
participants) for each experimental condition (color), as a function of offset
lag (in TRs). \textbf{B. Spatial autocorrelations.} The panel displays the
average correlation between the activation timeseries for each pair of nodes,
for each experimental condition (color), as a function of distance (in mm).  Error ribbons in
both panels denote bootstrap-estimated across-participant 95\% confidence intervals.}
\label{fig:autocorrs}
\end{figure}

@@

\clearpage
\newpage
\renewcommand{\refname}{Supplemental references}

\newcounter{bibcount}
\makeatletter
\patchcmd{\@lbibitem}{\item[}{\item[\hfil\stepcounter{bibcount}{\thebibcount.}}{}{}
\setlength{\bibhang}{2\parindent}
\renewcommand\NAT@bibsetup%
   [1]{\setlength{\leftmargin}{\bibhang}\setlength{\itemindent}{-\parindent}%
       \setlength{\itemsep}{\bibsep}\setlength{\parsep}{\z@}}
\makeatother

\bibliographystyle{apacite}
\bibliography{CDL-bibliography/cdl}
